\texttt{Anon}Dataset: A collection of benchmark datasets for learning with graphs

### 2020-06-07 main.tex
MC.

The papers~\cite{Fey+2019,Che+2019,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets. Recently, \url{ogb.stanford.edu}~\cite{Hu+2020} launched, however, the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point. Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions. http://www.jmlr.org/papers/volume21/18-370/18-370.pdf

>>>>

The papers~\cite{Fey+2019,Che+2019aa,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets. Recently, \url{ogb.stanford.edu}~\cite{Hu+2020} launched, however, the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point. Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions. http://www.jmlr.org/papers/volume21/18-370/18-370.pdf
